---
title: "Penguins"
author: "Roupen Khanjian"
output: html_document
params:
  species: unicorn
---

### Your job: create a parameterized report using data from `penguins.csv`. 

- Your report should contain a ggplot graph of flipper length versus body mass for the **species** that you choose.

- Create a function that will render the report for the species you pick, saved as an .html with format 'penguin_report_SPECIESNAME.html'. 

- Create a function that will automatically render a separate report for *all species* in the data. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

penguin_data <- read_csv("penguins.csv")

```



```{r, echo = FALSE}

penguin_subset <- penguin_data %>% 
  filter(species == params$species)

ggplot(data = penguin_subset, aes(x = body_mass_g, y = flipper_length_mm)) +
  geom_point(aes(color = sex))


```



```{r}

render_penguin_report = function(species) {
  rmarkdown::render(
    input = "your_turn.Rmd", # What's the input file to render?
    params = list(species = species), # What are the parameters?
    output_file = paste0("penguin_report_", species, ".html") # What should I name the output file?
  )
}

species_name <- unique(penguin_data$species)

map(species_name, render_penguin_report) # this works as well!!!

```

